TGI Spinal Analysis Code

### 2022-12-06 analysis/tgi-spinal_analysis.Rmd
plotting h2  - all the data

# plot the summary statistics
# first colours
blue <- brewer.pal(6, "Blues")
grey <- brewer.pal(6, "Greys")
purp <- brewer.pal(6, "Purples")
oran <- brewer.pal(6, "Oranges")
gren <- brewer.pal(6, "Greens")

@@

# plot
ggplot(h1_sum, aes(colour = quality, group = manipulation, alpha = manipulation)) + 
  geom_point(aes(condition, VAS), size = 2, position = position_dodge(-.3)) +
  geom_errorbar(aes(condition, ymin = VAS-ci, ymax = VAS+ci), width = .1, size = .7,
                position = position_dodge(-.3)) +
  geom_line(aes(condition, VAS), size = .7, position = position_dodge(-.3)) +
  facet_wrap(~quality) +
  scale_colour_manual(values = c(blue[4], oran[4], purp[4])) +
  scale_alpha_discrete(range = c(0.6, 1)) +
  ylim(0,50) +
  theme_bw() 
```

@@

# now plot the difference
ggplot(data = vas_h1_diff, aes(colour = quality)) +
  geom_hline(yintercept = 0, colour = 'grey50') +
  geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
             alpha = .5) +
  geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
             fill = 'grey15',
             shape = 21, size = 3) +
  geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
                                        ymax = difference+ci), 
                width = .1, size = .7, colour = 'grey15') +
  facet_wrap(~quality) +
  scale_colour_manual(values = c(blue[4], oran[4], purp[4])) +
  labs(title = 'Hypothesis 1: Segmental Distance',
       y = 'Within - Across VAS Ratings', x = NULL) +
  theme_classic() +
  theme(legend.position = 'none') -> h1_diff_plot

@@

Hypothesis 2 a & b: relative location of warm and cold
```{r h2}
# Summary statistics
h2_sum <- summarySEwithin(data = vas_meds, measurevar = 'VAS', 
                          withinvars = c('quality','manipulation','cold_probe'))

# organise data for plotting

# plot all data - half-violins

```

>>>>

# plot the summary statistics
# first colours
blue <- brewer.pal(8, "Blues")
grey <- brewer.pal(8, "Greys")
purp <- brewer.pal(8, "Purples")
oran <- brewer.pal(8, "Oranges")
gren <- brewer.pal(8, "Greens")

@@

# plot
ggplot(h1_sum, aes(colour = quality, group = manipulation, alpha = manipulation)) + 
  geom_point(aes(condition, VAS), size = 2, position = position_dodge(-.3)) +
  geom_errorbar(aes(condition, ymin = VAS-ci, ymax = VAS+ci), width = .1, size = .7,
                position = position_dodge(-.3)) +
  geom_line(aes(condition, VAS), size = .7, position = position_dodge(-.3)) +
  facet_wrap(~quality) +
  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
  scale_alpha_discrete(range = c(0.6, 1)) +
  ylim(0,50) +
  theme_bw() 
```

@@

# now plot the difference
ggplot(data = vas_h1_diff, aes(colour = quality)) +
  geom_hline(yintercept = 0, colour = 'grey50') +
  geom_point(aes(manipulation, difference, group = ID), position = position_dodge(.2),
             alpha = .5) +
  geom_point(data = h1_diff_sum, aes(manipulation, difference), colour = 'grey15',
             fill = 'grey15',
             shape = 21, size = 3) +
  geom_errorbar(data = h1_diff_sum, aes(manipulation, ymin = difference-ci,
                                        ymax = difference+ci), 
                width = .1, size = .7, colour = 'grey15') +
  facet_wrap(~quality) +
  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
  labs(title = 'Hypothesis 1: Segmental Distance',
       y = 'Within - Across VAS Ratings', x = NULL) +
  theme_classic() +
  theme(legend.position = 'none') -> h1_diff_plot

@@

Hypothesis 2 a & b: relative location of warm and cold
```{r h2}
# Summary statistics
# First, change name of manipulation
vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
h2_sum <- summarySEwithin(data = vas_meds, measurevar = 'VAS', 
                          withinvars = c('quality','manipulation','cold_probe'))

# organise data for plotting
vas_meds$cold_probe <- factor(vas_meds$cold_probe, levels = 
                                c('proximal', 'distal', 'rostral', 'caudal'))
h2_sum$cold_probe <- factor(h2_sum$cold_probe, levels = 
                                c('proximal', 'distal', 'rostral', 'caudal'))
# recoding cold probe location so can jitter
vas_meds$cold_code <- factor(vas_meds$cold_probe, labels = 
                                c(1,2,3,4))
h2_sum$cold_code <- factor(h2_sum$cold_probe, labels = 
                                c(1,2,3,4))
# creating jitter
vas_meds$xj <- jitter(as.numeric(vas_meds$cold_code), amount = .05)

nudge1 = -.1
nudge2 = .1

# plot all data - half-violins
# COLD
ggplot(data = vas_meds %>% 
         filter(quality == 'cold'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum %>% 
               filter(quality == 'cold'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum %>% 
               filter(quality == 'cold'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum %>% 
              filter(quality == 'cold'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(blue[4], blue[6])) +
  scale_fill_manual(values = c(blue[4], blue[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Cold ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_cold_plot

# WARM
ggplot(data = vas_meds %>% 
         filter(quality == 'warm'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum %>% 
               filter(quality == 'warm'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum %>% 
               filter(quality == 'warm'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum %>% 
              filter(quality == 'warm'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(oran[4], oran[6])) +
  scale_fill_manual(values = c(oran[4], oran[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Warm ratings', x = 'Location of cold probe', 
         y = NULL) +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_warm_plot

# BURN
ggplot(data = vas_meds %>% 
         filter(quality == 'burn'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum %>% 
               filter(quality == 'burn'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum %>% 
               filter(quality == 'burn'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum %>% 
              filter(quality == 'burn'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(purp[4], purp[6])) +
  scale_fill_manual(values = c(purp[4], purp[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Burn ratings', x = 'Location of cold probe', 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_burn_plot

# arrange entire plot
h2_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
                     nrow = 2, ncol = 2)
h2_plot

ggsave('h2_alldat_plot.png', h2_plot, device = NULL, path = anaPath,
       width = 10, height = 6.5, dpi = 600)
```
